---
title: "From Zero to Skill Demand"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{From Zero to Skill Demand}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}Sys.setenv(RAPIDAPI_KEY = "your_api_key_here")
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(skillgapR)
library(dplyr)
```


## Introduction

This vignette demonstrates how to use the `skillgapR` package to retrieve
job postings via the JSearch API and analyze job-market skill demand.

---

## Fetch job postings

The following example shows how to retrieve job postings using the JSearch API.
This step requires a valid RapidAPI key and is therefore not executed when
building the vignette.

```r
```{r, eval=FALSE}
jobs <- fetch_job_descriptions(
  query = "Data Scientist",
  location = "Canada"
)
```


---

## Example job data

For demonstration purposes, we use a small set of example job descriptions so
that the vignette can run without requiring API access.

```r
```{r}
jobs <- tibble::tibble(
  job_description = c(
    "python sql machine learning statistics",
    "data analysis python communication",
    "machine learning modeling cloud aws"
  )
)
```


---

## Analyze skill demand

```r
```{r}
skills <- analyze_skills(jobs)
head(skills)
```


---

## Visualize skill demand

```r
```{r}
plot_skill_demand(skills)
```


---

## Summary

This vignette illustrated an end-to-end workflow using `skillgapR`, from job
postings to skill demand analysis and visualization.
